### 2015-12-11 paper/3-features.tex
Proofread section 3.2

\subsection{Transparancy}
A user must only provide one model, implemented in C++11, which can be simulated by each synchronization kernel.
The exception is conservative synchronization: a lookahead function is required, whereas this is not possible in other synchronization kernels.
Two options are possible: either a lookahead function is always provided, even when it is not required and possibly not used, or using a default lookahead function if none is defined.

Always defining a lookahead function might seem redundant, especially if users will never use conservative synchronization.
The more attractive option is for the simulation tool to provide a default lookahead function, defined by the minimum detected time advance.
This lookahead value is most likely too small, but will prevent causality errors at the cost of performance.
Depending on the model, simulation performance might still be faster than sequential simulation.

Defining a lookahead function is therefore recommended in combination with conservative synchronization, but is not a necessity.

>>>>

\subsection{Transparancy}
We define simulation kernel transparancy as having a single model, which always can be executed on each supported synchronization kernel, without any modifications.
User should thus only provide one model, implemented in C++11, which can be either using sequential execution, using conservative synchronization, or using optimistic synchronization.
Switching between simulation kernels is as simple as altering the simulation termination time.
The exception is conservative synchronization, where a lookahead function is required, which is not used in other synchronization kernels.
Two options are possible: either a lookahead function must always be provided, even when it is not required and possibly not used, or we use a default lookahead function if none is defined.

Always defining a lookahead function might seem redundant, especially if users will never use conservative synchronization.
Especially since defining the lookahead is often non-trivial and dependent on intricate model details.
The more attractive option is for the simulation tool to provide a default lookahead function, such that simulation can run anyway, but maybe not at peak performance.
Depending on the model, simulation performance might still be faster than sequential simulation.

Defining a lookahead function is therefore recommended in combination with conservative synchronization, but is not a necessity, as a default can be used otherwise.
